---
output: rmarkdown::github_document
---

# speedtest

Tools to Test and Compare Internet Bandwidth Speeds

## Description

The 'Ookla' 'Speedtest' site <http://beta.speedtest.net/about> provides
interactive and programmatic services to test and compare bandwidth speeds from 
a source node on the Internet to thousands of test servers. Tools are provided
to obtain test server lists, identify target servers for testing and performing
speed/bandwidth tests.
    
## What's Inside The Tin

The following functions are implemented:

- `spd_best_servers`:	Find "best" servers (latency-wise) from master server list
- `spd_closest_servers`:	#' Find "closest" servers (geography-wise) from master server list
- `spd_config`:	Retrieve client configuration information for the speedtest
- `spd_download_test`:	Download test
- `spd_servers`:	Retrieve a list of SpeedTest servers

## TODO

Folks interested in contributing can take a look at the TODOs and pick as many as you like! Ones with question marks are truly a "I dunno if we shld" kinda thing. Ones with exclamation marks are essentials.

- [ ] Cache config in memory at startup vs pass around to functions?
- [ ] Figure out how to use beta sockets hidden API vs the old Flash API?
- [ ] Ensure the efficacy of relying on the cURL timings for speed measures for the Flash API
- [ ] Figure out best way to capture the results for post-processing
- [ ] Upload speed measures!
- [ ] Upload results to speedtest (tis only fair)!
- [ ] Incorporate more network or host measures for better statistical determination of the best target!
- [ ] `autoplot` support!
- [ ] RStudio Add-in
- [ ] CLI wrapper
- [ ] Shiny app?

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/speedtest")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(speedtest)

# current verison
packageVersion("speedtest")

```

